A Formal Verification Framework for Smart Contracts Based on Symbolic Execution

### 2024-01-17 papers/static-checker/ecoop2024/ecoop2024.tex
kolibri specification

\begin{lstlisting}[float=tp,captionpos=b,caption={Specification of the \lstinline/approve/ entrypoint (Property 1)},label={lst:specification-approve-1},numbers=left]
entrpoint %approve
   parameter := Pair (spender: address) (value: nat)
   pre-condition := not (paused = true)
      && get_big_map (Sender, ledger) = 
        Some (v: pair nat (map address nat))
      && v = Pair (n: nat) (m: map address nat) 
      && get_map (spender, m) = Some (k: nat) 
      && not (k = 0) | (value = 0)
   post-condition := get_big_map (Sender, post_ledger) = 
        Some (post_v:  (pair nat (map address nat))
      && post_v = Pair (post_n: nat) (post_m: map address nat) 
      && get_map (spender, post_m) = Some (post_k: nat) 
      && (post_k = 0) ;
\end{lstlisting}
\begin{lstlisting}[float=tp,captionpos=b,caption={Specification of the \lstinline/approve/ entrypoint (Property 2)},label={lst:specification-approve-2},numbers=left]
   pre-condition := not (paused = true) 
      && get_big_map (Sender, ledger) = 
        Some (v: option (pair nat (map address nat))) 
      && v = Pair (n: nat) (m: map address nat) 
      && get_map (spender, m) = Some (k: nat) 
      && (k = 0) | not (value = 0)
   post-condition := get_big_map (Sender, post_ledger) = 
        Some (post_v: option (pair nat (map address nat))) 
      && post_v = Pair (post_n: nat) (post_m: map address nat) 
      && get_map (spender, post_m) = Some (post_k: nat) 
      && (post_k = value) ;
\end{lstlisting}

>>>>

\begin{lstlisting}[float=tp,captionpos=b,caption={Specification of the \lstinline/approve/ entrypoint (Property 1)},label={lst:specification-approve-1},numbers=left]
entrpoint %approve
   parameter := Pair (spender: address) (value: nat)
   pre-condition := not (paused = true)
      && get_big_map (Sender, ledger) = 
        Some (v: pair nat (map address nat))
      && v = Pair (n: nat) (m: map address nat) 
      && get_map (spender, m) = Some (k: nat) 
      && not (k = 0) && (value = 0)
   post-condition := get_big_map (Sender, post_ledger) = 
        Some (post_v:  (pair nat (map address nat))
      && post_v = Pair (post_n: nat) (post_m: map address nat) 
      && get_map (spender, post_m) = Some (post_k: nat) 
      && (post_k = 0) ;
\end{lstlisting}
\begin{lstlisting}[float=tp,captionpos=b,caption={Specification of the \lstinline/approve/ entrypoint (Property 2)},label={lst:specification-approve-2},numbers=left]
   pre-condition := not (paused = true) 
      && get_big_map (Sender, ledger) = 
        Some (v: option (pair nat (map address nat))) 
      && v = Pair (n: nat) (m: map address nat) 
      && get_map (spender, m) = Some (k: nat) 
      && (k = 0) && not (value = 0)
   post-condition := get_big_map (Sender, post_ledger) = 
        Some (post_v: option (pair nat (map address nat))) 
      && post_v = Pair (post_n: nat) (post_m: map address nat) 
      && get_map (spender, post_m) = Some (post_k: nat) 
      && (post_k = value) ;
\end{lstlisting}
